---
title: "Seat vs. Major"
author: "Tara"
date: "November 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 

Question: Does it matters where one sits in the classroom , by ones major?
 Study shows that a small percent of Liberal Arts students siti in the front, middle , and the back of a classroom. There is a large percentage of Non liberal
 Arts student that sits in al seats.
 
 



```{r include=FALSE}
require(tigerstats)
require(tidyverse)
data(ucdavis1)
#View(ucdavis1)
```

##Look at Seat vs. Major


```{r}
seatmajor=xtabs(~Seat + class, data=ucdavis1)
barchartGC(seatmajor,type="percent")
```
##Data:

There are two catergorical variables seats and class, seats has three rows, front, middle. and back. The class has two levels Liberal Arts, and Non Liberal Arts students.


  
The following graph shows 80% of "Non Liberal Arts" sits in all areas in the classroom. There is a 15% of "Liberal Arts" students that sits in three areas of the class.


```{r}
rowPerc(seatmajor)
```

##Summary:

$H_O$: There is no evidence relationship to where ones sits in a classroom, and his major.  
$H_A$:   Where one sits in the classroom and his major is related.











```{r}
chisqtestGC(seatmajor,simulate.p.value=TRUE)
```






